---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spiR

Client for Social Progress Index Data

<!-- badges: start -->
<!-- badges: end -->

The goal of spiR is to allow an easy connection with R to the Social Progress Index

## Installation

You can install the released version of spiR from [CRAN](https://CRAN.R-project.org) with:

```{r, eval = FALSE}
install.packages("spiR")
```


## Examples


sqs_spi_data(country = c("USA", "FRA"), years = "2018", )
sqs_spi_data(country = c("USA", "FRA"), year = c("2018", "2019"), indicators = "SPI")
sqs_spi_data("USA", "2019", c("SPI", "FOW"))
sqs_spi_data(, "2018", )
sqs_spi_data("USA", "2017", )
sqs_spi_data("USA", , )
sqs_spi_data(, , )
sqs_spi_data()

sqs_spi_country()
sqs_spi_country(country = "Canada")
sqs_spi_country("Canada")

sqs_spi_indicator()
sqs_spi_indicator(indicators = "mortality")
sqs_spi_indicator("mortality")

